% Ubah judul dan label berikut sesuai dengan yang diinginkan.
\section{Introduction}
\label{sec:introduction}

% Ubah paragraf-paragraf pada bagian ini sesuai dengan yang diinginkan.

The use of trucks as a mode of goods transportation in Indonesia continues to increase each year. According to data from the Central Bureau of Statistics in 2023 \cite{bps2023}, trucks are the third most numerous vehicles after motorcycles and passenger cars, with significant numbers across various provinces. However, the use of trucks as a mode of goods transportation also creates negative impacts, one of which is traffic accidents. Based on the journal Analysis of the Effect of ODOL (Overdimension Overloading) Vehicles on Accident Rates on Toll Roads \cite{odol2020}, it was found that the influence of ODOL vehicles on accident rates on toll roads was proven to be 32\%, with the remainder being other factors. Losses from ODOL accidents also cause a decrease in the average vehicle speed on toll roads by 12\%.

In addition, ODOL inspections by UPPKB (Motor Vehicle Weighing Implementation Unit) stated that in 2023, the average number of vehicles that entered and were inspected was only around 5\%. Of this number, 27.95\% of vehicles were found to have committed violations. The majority of violations were related to excess cargo, reaching 69\%, while the remaining 31\% were related to document violations. Vehicles that violate load regulations carry an average excess load of between 5\% and 20\% of the permitted capacity \cite{hubdat2024}. This condition shows that manual inspection methods have limitations and are not effective enough to significantly reduce violations.

Therefore, an automated system is needed that can detect violations in real-time, increase monitoring coverage, and provide direct notifications to users. This system must be able to identify vehicles that violate permitted dimension limits, using deep learning technology, specifically Convolutional Neural Network (CNN). Implementation of deep learning models on edge devices will enable the system to run in real-time and can be applied to various locations without requiring complex infrastructure.

Overdimension violations in motor vehicles represent a serious problem that can cause both economic and safety losses. However, the manual inspection methods currently used by UPPKB have limitations and are not effective enough to significantly reduce violations. Therefore, an automatic detection system is needed that can detect overdimension vehicles in real-time with high accuracy and optimal efficiency. Based on this background, the research problems addressed in this study are how to implement a detection system that can run on edge devices, how to create a scalable detection system that can be integrated with existing systems, and how to add automatic notification features to authorities when overdimension violations occur.

The main objectives of this research are to implement a detection system that can run on edge devices, to create a scalable detection system that can be integrated with existing systems, and to add automatic notification features to authorities when overdimension violations occur. This research focuses on using deep learning models, specifically Convolutional Neural Network (CNN), to detect overdimension vehicles in real-time. The limitations of this study include restrictions to specific deep learning models for detecting overdimension vehicles without exploring other models, and initial system testing may be conducted in a controlled environment, but is expected to be applicable to various locations with different conditions.

The benefits obtained from this research include contributing to the development of overdimension vehicle detection technology using deep learning models, providing effective and efficient solutions in detecting overdimension vehicles in real-time, and providing recommendations for further research in the development of overdimension vehicle detection systems.