\section*{Acknowledgments}

The author would like to express sincere gratitude to Mr. Arief Kurniawan as the Head of Computer Engineering Department, Faculty of Intelligent Electrical and Informatics Technology, Institut Teknologi Sepuluh Nopember and as the First Supervisor and Mrs. Diah Puspito Wulandari as the Second Supervisor who have provided guidance and assistance to the author during the completion of this final project. All lecturers of the Computer Engineering Department, for the knowledge imparted to the author throughout the course of study. Parents, Siblings, Grandfather, Grandmother, and family who have provided prayers and support during the author's education. East Java Province Transportation Department for granting permission for data collection on Tanjung Perak Road. PT Jasa Marga as the manager of Dupak 2 Toll Gate who has granted permission for system implementation at Dupak 2 Toll Gate. Friends in the Multimedia and Internet of Things (MIOT) laboratory who assisted the author in completing this final project. Close friends who were always present, providing moral support, motivation, and companionship through the ups and downs during the process of completing this final project. Fellow Computer Engineering students who provided motivation and encouragement throughout the academic journey. Friends in the Multimedia and Internet of Things (MIOT) laboratory who assisted the author in completing this final project. Close friends who were always present, providing moral support, motivation, and companionship through the ups and downs during the process of completing this final project. Fellow Computer Engineering students who provided motivation and encouragement throughout the academic journey. 